\section{Oppgaver 13. Februar}

\subsection{Assignments 1} 
done
\subsection{Assignments 2}
done
\subsection{Assignments 3}
done
\subsection{Assignments 4} 
error log, query log, binary log, slow query log, mysqldump
%/var/log/mysql.log /var/log/mysql/mysql.log /var/log/mysql/mysql-slow.log /var/log/mysql/error.log

\subsection{Assignments 5} 
\#!/bin/bash\\

DATE=\$(date +"\%y\%m\%d\%H\%M");\\

function backup() \{\\
dir="/home/ubuntu/backups/\$1/"\\
file="/home/ubuntu/backups/\$1/\$DATE"\\
        if ls \$dir > /dev/null; then\\
                cp \$2 \$file\\
        else\\
                mkdir \$dir;\\
                cp \$2 \$file;\\
        fi\\
\}\\

\#(type)(path)\\
backup "errorlog" "/var/log/syslog"\\
\#insert all log files:\\

tar cvzf "/home/ubuntu/backup-\$DATE.tar.gz" /home/ubuntu/backups/\\

scp /home/ubuntu/backup-\$DATE.tar.gz ubuntu@10.10.1.176:/mnt/backup/

\subsection{Assignments 6} 
\begin{enumerate}
\item Files to rotate can be set by giving their path (/var/log/mysql.log, /var/log/mysql/mysql.log /var/log/mysql/mysql-slow.log /var/log/mysql/error.log)
\item Files can be rotated daily, weekly, monthly or yearly by adjusting the rotation interval parameter. The logs can also be rotated because of a set log file size (set to every day, 7 times before being removed)
\item The rotate count paramater determines how many log files that should be kept before the oldest are deleted.
\end{enumerate}
	

\subsection{Assignment 9} 
When taking backups locally before sending it to another machine, you ensure that the backup exists before shipping it off. If it's being transmitted during the time of backup, chances for getting a corrupted file is greater; on the other hand, if sending it off to another machine straight away, less available space is required on the sending machine, and full logs don't necessarily have to be stored on the machine itself. 


\subsection{Assignments 9} 
You are not able to compress the data by backing up the mysqldump from a remote machine. The user also needs quite a lot of permissions to perform the remote backup.\\
Performing the backup remotly might be easier to automate, depending on the setup.

\subsection{Assignments 10} 
mysqlbinlog mysql-bin.* > binlog.sql

or 

mysqladmin flush-logs (flushing the log causes the creation of a new one)

\subsection{Assignments 11} 
yes

\subsection{Assignments 14} 

\subsection{Assignments 15}
Each 7th day, a snapshot should be taken of the whole system. This will give time to do a full back up of the whole database and all necessary logs.\\
All log files should also be backed up daily. Backup logs should be kept for aslong as possible, but atleast for a minimum of 30days. Each time a log is backed up, the log start in a new file, to prevent redundant backups.

\subsection{Assignments 16}
\begin{enumerate}
\item We would start by restoring most of the data from the most recent mysqldump. Then we would manually go through the binlogs and remove all the stuff we don't want to happen again, before replaying the binlog and inserting all the newest entries.
\item A snapshot of a completly configured and set up machine should be taken of every type of server we have. A snapshot should also be taken of all systems each week and stored for a limted time. This means we will always have a snapshot of the server that is maximum 7days old at worst. All changes made to a system is also documented, so recreating all that is missing should not be too hard, though it might be time consuming.
\end{enumerate}

\subsection{Assignments 17}
